Patient movements

### 2024-12-09 analysis/patient-tracking.Rmd
final cosmetic changes

# filter considered clinical attendees
df_matched <- do.call(
  rbind,
  lapply(
    unique(df$date),
    function(d) {
      readRDS(paste0(
        "data-clean/patient-tracking/matched-clinical/",
        d, ".rds"
      ))
    }
  )
) %>%
  mutate(
    date = as.Date(time),
    hr = lubridate::hour(time)
  ) %>%
  filter(between(hr, 8, 15)) %>%
  filter(!(hr > 11 & date == "2021-10-15")) %>%
  group_by(date, patient_id) %>%
  slice(1) %>%
  ungroup() %>%
  mutate(patient_id = paste(date, patient_id))

@@

@@

@@

>>>>

# filter considered clinical attendees
df_matched <- do.call(
  rbind,
  lapply(
    unique(df$date),
    function(d) {
      readRDS(paste0(
        "data-clean/patient-tracking/matched-clinical/",
        d, ".rds"
      )) %>% dplyr::select(patient_id, time)
    }
  )
) %>%
  mutate(
    date = as.Date(time),
    hr = lubridate::hour(time)
  ) %>%
  filter(between(hr, 8, 15)) %>%
  filter(!(hr > 11 & date == "2021-10-15")) %>%
  group_by(date, patient_id) %>%
  slice(1) %>%
  ungroup() %>%
  mutate(patient_id = paste(date, patient_id))

@@

saveRDS(
  time_in_clin_pl,
  "results/data/time-in-clinic.rds"
)

@@

saveRDS(
  time_pl,
  "results/data/no-people-over-time.rds"
)

@@

saveRDS(
  spatial_pl,
  "results/data/no-people-spatial.rds"
)
